### 2020-06-04 report/sections/introduction/contributions.tex
Report: small fixes
Report: minor changes

In \cref{chap:p2p}, we introduce the \fancyname{TwoBuyer} multiparty
protocol to motivate our proposal of providing the server role with 
routing responsibilities in addition to its existing interactions
specified in the protocol.

>>>>

In \cref{chap:p2p}, we introduce the \tprotocol{Two Buyer} multiparty
protocol to motivate our proposal of providing the server role with 
routing responsibilities in addition to its existing interactions
specified in the protocol.
